Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Defined Mass Windows

### 2017-03-02 paper.tex
add some text

>>>>

The initial notch search is significantly faster than a corresponding wide mass search, and this suggests that multiple search rounds could be conducted, iteratively adding more and more modifications.
This recursive nature of the algorithm is well suited to add multiple modifications of different types on the same peptide.
Due to these enhancements, we test the performance of our methods

\begin{table}[]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
                      &        & \multicolumn{2}{l|}{Single Round}                                                                              & \multicolumn{2}{l|}{Multiple Rounds}                                                                           \\ \hline
                      &        & \begin{tabular}[c]{@{}l@{}}Mods:\\ none\end{tabular} & \begin{tabular}[c]{@{}l@{}}Mods:\\ ptmlist\end{tabular} & \begin{tabular}[c]{@{}l@{}}Mods:\\ none\end{tabular} & \begin{tabular}[c]{@{}l@{}}Mods:\\ ptmlist\end{tabular} \\ \hline
\multirow{2}{*}{PSMs} & Jurkat &                                                      &                                                         &                                                      &                                                         \\ \cline{2-6} 
                      & Mouse  &                                                      &                                                         &                                                      &                                                         \\ \hline
\multirow{2}{*}{Mods} & Jurkat &                                                      &                                                         &                                                      &                                                         \\ \cline{2-6} 
                      & Mouse  &                                                      &                                                         &                                                      &                                                         \\ \hline
\multirow{2}{*}{Time} & Jurkat &                                                      &                                                         &                                                      &                                                         \\ \cline{2-6} 
                      & Mouse  &                                                      &                                                         &                                                      &                                                         \\ \hline
\end{tabular}
\end{table}
